### 2023-01-25 manuscript.tex
lualatex [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/2a8b4df20b46456e0a64f573b633682c1b8abbd8.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/2a8b4df20b46456e0a64f573b633682c1b8abbd8/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4001955882

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/9a7ff254f386b2d4c6b95bea2ca71d9e215395b0/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/9a7ff254f386b2d4c6b95bea2ca71d9e215395b0}{stain/2022-fdo-paper@9a7ff25}
on January 25, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/2a8b4df20b46456e0a64f573b633682c1b8abbd8/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/2a8b4df20b46456e0a64f573b633682c1b8abbd8}{stain/2022-fdo-paper@2a8b4df}
on January 25, 2023.
